---
title: "Blood Transfusion Analysis"
output: html_notebook
---

In this project, you will leverage your knoweldge of hypothesis testing to help drive informed decisions at a company inspecting blood transfusion data, Familiar.

You will use your combined knowledge of R and hypothesis testing to implement an analysis. The project will require implementation of standard deviation, one and two sample t-tests, as well as an understanding of the significance on the resulting p-value to give a recommendation on the results of the study.

# One Sample T-Test

```{r error=TRUE}
# load data
vein_lifespans <- c(76.93767, 75.99336, 74.79815, 74.50202, 77.48889, 72.14257, 75.99303, 76.34155, 77.48476, 76.53210, 76.25509, 77.58398, 77.04737, 72.87475, 77.43505, 77.49234, 78.32672, 73.34370, 79.96916, 74.83801)
artery_lifespans <-c(6.33537, 76.92308, 75.95244, 74.54498, 76.40450, 73.07925, 77.02354, 74.11742, 77.38651, 73.04477, 74.96312, 73.31954, 75.85740, 76.15265, 73.35510, 73.90221, 73.77121, 68.31490, 74.63976, 78.38548)
```

1.  Familiar want to know if their most basic package, the Vein Pack, actually has a significant impact on the subscribers. It would be a marketing goldmine if it could show that subscribers to the Vein Pack live longer than the general public. Lifespans of Vein Pack users are given in the variable `vein_lifespans`, which has been loaded into `notebook.Rmd`. View `vein_lifespans`.

```{r error=TRUE}
# view vein_lifespans here:
vein_lifespans
```

2.  You’d like to find out if the average lifespan of a Vein Pack subscriber is *significantly different* from the average life expectancy of `71` years. Begin by finding mean lifespan of users of the Vein Pack, and save the result to `vein_lifespans_mean`. View `vein_lifespans_mean`.

```{r error=TRUE}
# calculate vein_lifespans_mean here:
vein_lifespans_mean <- mean(vein_lifespans)

vein_lifespans_mean
```

3.  Now find the standard deviation of the lifespan of users of the Vein Pack. Save the result to `vein_lifespans_sd`, and view it

```{r error=TRUE}
# calculate vein_lifespans_sd here:
vein_lifespans_sd <- sd(vein_lifespans)

vein_lifespans_sd
```

4.  Use a One Sample T-Test to compare `vein_lifespans` to the average life expectancy, `71`. Save the result into a variable called `vein_pack_test`, and view it. Are the results significant? Check the p-value of `vein_pack_test`. If it’s less than `0.05`, the standard threshold, you’ve got significance!

```{r error=TRUE}
# perform one sample t-test here:
vein_pack_test <- t.test(vein_lifespans, mu = 71)

vein_pack_test

# Therefore Reject the Null Hypothesis
```

# Two Sample T-Test

5.  In order to differentiate Familiar’s product lines, they would like you to compare the lifespan data for the Vein Pack with their more premium product, the Artery Pack.

Lifespans of Artery Pack users are given in the variable `artery_lifespans`, which has been loaded into `notebook.Rmd`. View `artery_lifespans`.

```{r error=TRUE}
# view artery_lifespans here:
artery_lifespans
```

6.  Before you run a Two Sample T-test to compare the Vein Pack and the Artery pack, you want to learn more about the data collected on users of the Artery pack.

Begin by finding mean lifespan of users of the Artery Pack, and save the result to `artery_lifespans_mean`. View `artery_lifespans_mean`.

```{r error=TRUE}
# calculate artery_lifespans_mean here:
artery_lifespans_mean <- mean(artery_lifespans)

artery_lifespans_mean
```

7.  Now find the standard deviation of the lifespan of users of the Artery Pack.

Save the result to `artery_lifespans_sd`, and view it.

```{r error=TRUE}
# calculate artery_lifespans_sd here:
artery_lifespans_sd <- sd(artery_lifespans)

artery_lifespans_sd
```

8.  Use a Two Sample T-Test to compare `vein_lifespans` to `artery_lifespans`. Save the result into a variable called `package_comparison_results`, and view it.

Are the results significant? Check the p-value of `package_comparison_results`. If it’s less than `0.05`, the standard threshold, you’ve got significance!

```{r error=TRUE}
# perform two sample t-test here:
package_comparison_results <- t.test(vein_lifespans, artery_lifespans)

package_comparison_results

# Fail to Reject the Null Hypothesis
```
